---
title: "Gapmider"
author: "Nithin"
date: "20/01/2022"
output: 
  bookdown::html_document2:
    keep_md: yes
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	fig.topcaption=TRUE
)
library(tidyverse)
library(gapminder)
library(knitr)
```
# Continent wise analysis of gapminder data
```{r,message=FALSE,warning=F,include=FALSE}
plot_fn<-function(continent){
       gapminder %>% 
    filter(continent == eval(continent),
           year == 1952) %>% 
    ggplot(aes(x = pop,
               y = gdpPercap)) +
    geom_point()   
}

```

```{r,echo=FALSE,results='asis'}
src=map(levels(unique(gapminder$continent)),function(continent){
        knitr::knit_expand(text = c(
                "## Gapminder for {{continent}}",
                "```{r gg-gapminder-{{tolower(continent)}}-scatter, fig.cap='Scatter plot for {{continent}}',dev='jpeg'}",
                "plot_fn(continent)",
                "```"
        ))
})
res=knitr::knit_child(text=unlist(src),quiet=T)
cat(res,sep = "\n")
```

# Objective
generate code chunks , so that I can use internal cross-referencing properly.

## Mannual Method
````
```{r gg-gapminder-europe-scatter, fig.cap="Scatter plot for Europe",,dev='jpeg'}`r ''` 
plot_fn(Europe)
```
````
This has to be repeated for all the continents. Now for referencing figure for Africa, we can do something like this
-Figure \@ref(fig:gg-gapminder-africa-scatter) 

## Programmatic Insertion

To programmatically insert these we need `knitr::knit_expand()` and `purrr::map`


